Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-11-28 manuscript/manuscript.tex
Fix spherical shell analytical solutions for exp density

From Eq. \ref{eq:shell-pot} we can obtain expressions of the gravitational potential for
different density functions.
For a linear density function

@@

An exponential density function that assumes the values of $\rho_\text{out}$ and
$\rho_\text{in}$ on the shell's outer and inner surfaces, respectively, can be defined
as follows:

\begin{equation}
    \rho(r') = A e^{-(r' - R)/b} + C,
\end{equation}

@@

\begin{equation}
    A = (\rho_\text{in} - \rho_\text{out})
        \left( e^{( R_2 - R_1 )/b} - 1 \right)^{-1},
\end{equation}

\begin{equation}
    C = \rho_\text{out} - A,
\end{equation}

\noindent $R$ is the mean Earth radius, and $b$ is a constant
that determines the variability of the function: a low value of $b$
increases the maximum slope of the density function.

The analytical solution of the gravitational potential generated by a
spherical shell with a density function is

\begin{equation}
    \begin{split}
        V_\text{sh}^\text{exp}(r) = \frac{4\pi G}{r}
        Ab
        \Big[
        & (R_1^2 + 2R_1 b + 2b^2)e^{-\frac{R_1 - R}{b}} - \\
        & (R_2^2 + 2R_2 b + 2b^2)e^{-\frac{R_2 - R}{b}}
        \Big] + \\
        & \frac{4 \pi G}{3 r} C (R_2^3 - R_1^3).
    \end{split}
\label{eq:shell-pot-exp}
\end{equation}

>>>>

From Eq. \ref{eq:shell-pot} we can obtain expressions of the gravitational potential for
different density functions.

\subsection{Linear density}

For a linear density function

@@

\subsection{Exponential density}

For an exponential density function

\begin{equation}
    \rho(r') = A e^{- k (r' - R)},
\end{equation}

\noindent
where $A$, $k$ and $R$ are constants, the gravitational potential on any external point
is

\begin{equation}
    \begin{split}
    V_\text{exp}(r) = \frac{4\pi G}{r} \frac{A}{k^3} \Big[
    & \left( R_1^2 k^2 + 2 R_1 k + 2 \right) e^{- k (R_1 - R)} - \\
    & \left( R_2^2 k^2 + 2 R_2 k + 2 \right) e^{- k (R_2 - R)}
    \Big].
    \end{split}
\end{equation}

Moreover, an exponential density function that assumes the values of $\rho_\text{out}$
and $\rho_\text{in}$ on the shell's outer and inner surfaces, respectively, can be
defined as follows:

\begin{equation}
    \rho(r') = A e^{- \frac{b}{T} (r' - R)} + C,
\end{equation}

@@

\begin{equation}
    A = \frac{\rho_\text{in} - \rho_\text{out}}{D},
\end{equation}

\begin{equation}
    C = \frac{1}{D}
    \left[\rho_\text{out} \, e^{- \frac{b}{T} (R_1 - R)} -
    \rho_\text{in} \, e^{- \frac{b}{T} (R_2 - R)} \right],
\end{equation}

\begin{equation}
    D = e^{- \frac{b}{T} (R_1 - R)} - e^{- \frac{b}{T} (R_2 - R)},
\end{equation}

\noindent $R$ is the mean Earth radius, $T$ is the thickness of the shell ($T = R_2
- R_1$) and $b$ is a dimensionless constant that determines the variability of the
function: a high value of $b$ increases the maximum slope of the density function.

The analytical solution of the gravitational potential generated by a
spherical shell with such density function is

\begin{equation}
    \begin{split}
        V_\text{exp}(r) = & \frac{4\pi G}{r} \frac{A T^3}{b^3} \\ \Big[
        & \left( \left( b R_1/T \right)^2 + 2 b R_1/T + 2 \right)
        e^{- \frac{b}{T} (R_1 - R)} - \\
        & \left( \left( b R_2/T \right)^2 + 2 b R_2/T + 2 \right)
        e^{- \frac{b}{T} (R_2 - R)}
        \Big] + \\
        & \frac{4\pi G}{3 r} C \left( R_2^3 - R_1^3 \right).
    \end{split}
\label{eq:shell-pot-exp}
\end{equation}
